### 2014-11-07 tex/definitions.tex
Grouped Figure 8 and Figure 9

\begin{definition}
\label{representation}
The \textbf{representation relation} $\sqsubset$ is defined as
follows: given state $s_p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$
and state $s_q = (
\cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$,
$s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
(\cfgnt{L}_q\ \cfgnt{R}_q)$ such that
\begin{equation}
\label{eqn:valid}
 \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
\end{equation}
The represented relation is extended to sets of states $P$ and $Q$ as
$$
P \sqsubset Q \Longleftrightarrow \forall q \in Q\ (\forall p \in S\ (p \sqsubset q \Rightarrow p \in P))
$$
\end{definition}

\begin{definition}
\label{def:meta}
A state relation $p \rightarrow_x q$ is extended to sets of states $P \hookrightarrow_x Q$ as
$$
P \hookrightarrow_x Q \Longleftrightarrow \forall q \in S\ (p \rightarrow_x q \Rightarrow q \in Q)
$$
The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\ell \wedge \hookrightarrow_\com$, and 
the $\rsym$ relation extended to sets of states is 
$$
\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
$$
\end{definition}

\begin{definition}
\label{bisimulation}
The functional associated to bisimulation,  $F_\sim(\sqsubset)$, is the set of all pairs of sets of states
$(P\ Q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists Q^\prime\ ( (Q \rssym Q^\prime )\wedge (P^\prime\ \sqsubset\ Q^\prime )))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall Q^\prime\ ( Q \rssym Q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ P^\prime )))
\end{equation}
The bisimularity relation is the greatest fixed point of the functional.
\end{definition}

>>>>

\begin{definition}
\label{representation}
The \textbf{representation relation} $\sqsubset$ is defined as
follows: given state $s_p = (
\cfgnt{L}_p\ \cfgnt{R}_p\ \phi_p\ \eta_p\ \cfgnt{e}_p\ \cfgnt{k}_p )$
and state $s_q = (
\cfgnt{L}_q\ \cfgnt{R}_q\ \phi_q\ \eta_q\ \cfgnt{e}_q\ \cfgnt{k}_q )$,
$s_p \sqsubset s_q $ if and only if $\eta_p = \eta_q ,\ \cfgnt{e}_p =
\cfgnt{e}_q ,\ \cfgnt{k}_p = \cfgnt{k}_q$, and there exists a
homomorphism $(\cfgnt{L}_p\ \cfgnt{R}_p) \rightharpoonup_{h}
(\cfgnt{L}_q\ \cfgnt{R}_q)$ such that
\begin{equation}
\label{eqn:valid}
 \mathbb{S}( \phi_q \wedge \mathbb{HC}(s_p \rightharpoonup_{h} s_q) ) 
\end{equation}
The represented relation is extended to sets of states $P$ and $Q$ as
$$
P \sqsubset Q \Longleftrightarrow |Q| = 1 \wedge \forall q \in Q\ (\forall p\ (p \sqsubset q \Rightarrow p \in P))
$$
\end{definition}

\begin{definition}
\label{def:meta}
A state relation $p \rightarrow_x p^\prime$ is extended to sets of states $P \hookrightarrow_x P^\prime$ as
$$
P \hookrightarrow_x P^\prime \Longleftrightarrow \forall p^\prime\ (p \rightarrow_x p^\prime \Rightarrow p^\prime \in P^\prime)
$$
The $\rgse$ relation over sets of states is $\rsgse = \hookrightarrow_\ell \cup \hookrightarrow_\com$, and 
the $\rsym$ relation extended to sets of states is 
$$
\rssym = \hookrightarrow_\mathit{FA} \cup \hookrightarrow_\mathit{FW} \cup \hookrightarrow_\mathit{EQ}^T \cup \hookrightarrow_\mathit{EQ}^F \cup \hookrightarrow_\com
$$
\end{definition}

\begin{definition}
\label{bisimulation}
The functional associated to bisimulation,  $F_\sim(\sqsubset)$, is the set of all pairs of sets of states
$(P\ Q)$ such that
\begin{equation}
\label{eqn:BisimulationForwards}
\forall P^\prime\ ( P \rsgse P^\prime \Rightarrow \exists Q^\prime\ ( (Q \rssym Q^\prime )\wedge (P^\prime\ \sqsubset\ Q^\prime )))
\end{equation}
\begin{equation}
\label{eqn:BisimulationBackwards}
\forall Q^\prime\ ( Q \rssym Q^\prime\Rightarrow \exists P^\prime\ ( (P \rsgse P^\prime )\wedge (P^\prime\ \sqsubset\ Q^\prime )))
\end{equation}
The bisimularity relation is the greatest fixed point of the functional.
\end{definition}

### 2014-11-07 tex/proofs.tex
Grouped Figure 8 and Figure 9

%we need to define how r' is arrived at for this one to work...
\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If two field access states are related in the represented by relation,
then they are also related in the functional associated to bisumlation.
\label{lem:access}
$$
\forall p \in S_\mathit{FA}\ (\forall q \in S_\mathit{FA}\ (p \sqsubset q \Rightarrow (p\ q) \in F_\sim(\sqsubset)))
$$
\end{lemma}

>>>>

%we need to define how r' is arrived at for this one to work...
\begin{lemma}[\textrm{F{\footnotesize IELD}} \textrm{A{\footnotesize CCESS}} preserves $\sqsubset\ \subseteq F_\sim(\sqsubset)$]
If two sets of field access states are related in the represented by relation,
then they are also related in the functional associated to bisumlation.
\label{lem:access}
$$
\forall p \in S_\mathit{FA}\ (\forall q \in S_\mathit{FA}\ (p \sqsubset q \Rightarrow (p\ q) \in F_\sim(\sqsubset)))
$$
\end{lemma}
